The LHC as a Neutrino-Ion Collider

### 2023-09-27 journal_sub/main.tex
Add epjc typeset version

\documentclass[11pt,a4paper]{article}
\pdfoutput=1

\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}

\usepackage{placeins,cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{afterpage}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{url}
\usepackage{booktabs,multirow}
\usepackage{textcomp}
\graphicspath{{../}{./figures/}}

\makeatletter
\def\thickhline{%
             \noalign{\ifnum0 =`}\fi\hrule \@height \thickarrayrulewidth \futurelet
             \reserved@a\@xthickhline}
\def\@xthickhline{\ifx\reserved@a\thickhline
                \vskip\doublerulesep
                \vskip -\thickarrayrulewidth
                \fi
                \ifnum0 =`{\fi}}
\makeatother
\newlength{\thickarrayrulewidth}
\setlength{\thickarrayrulewidth}{3\arrayrulewidth}

@@

\begin{document}
\newgeometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,bindingoffset=0mm}

\vspace{-2.0cm}
\begin{flushright}
Nikhef-2023-009 \\ CERN-TH-2023-165\\
\end{flushright}
\vspace{0.6cm}

\begin{center}
  {\Large \bf The LHC as a Neutrino-Ion Collider}\\
  \vspace{1.1cm}
  {\small
    Juan M. Cruz-Martinez$^{1}$, Max Fieg$^{2}$, Tommaso Giani$^{3,4}$, Peter Krack$^{3,4}$, Toni M\"akel\"a$^{5}$,  \\[0.1cm]
    Tanjona Rabemananjara$^{3,4}$, and Juan Rojo$^{3,4}$
  }\\

\vspace{0.7cm}

{\it \small
    ~$^1$CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland \\[0.1cm]
    ~$^2$ Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA  \\[0.1cm]
    ~$^3$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
    ~$^4$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
    ~$^5$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
 }

\vspace{1.0cm}

{\bf \large Abstract}

\end{center}

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS)
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
for FASER$\nu$ and SND@LHC at Run III,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
%
We determine that up to one million electron- and muon-neutrino DIS interactions
within detector acceptance can be expected by the end of the HL-LHC,
covering a kinematic region in $x$ and $Q^2$ overlapping with that
of the Electron-Ion Collider.
%
Including these DIS projections into
global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
for strangeness and the up and down valence PDFs.
%
We show that LHC neutrino data enables improved theoretical
predictions for core processes at the HL-LHC, such as Higgs and weak gauge
boson production.
%
Our analysis demonstrates that exploiting the LHC neutrino beam effectively
provides CERN with a ``Neutrino-Ion Collider''
without  requiring modifications in its accelerator infrastructure.

\clearpage

\tableofcontents
\input{sec-introduction}
\input{sec-dis-pseudodata}
\input{sec-results}
\input{sec-pheno}
\input{sec-summary}
\appendix
\input{app-faser.tex}
\input{app-nuclearPDFs.tex}

\bibliographystyle{utphys}
%\bibliography{FPF-WG1}
\input{FPF-WG1.bbl}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for The European Physical Journal
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{filecontents}{leer.eps}
	%!PS-Adobe-2.0 EPSF-2.0
	%%CreationDate: Mon Jul 13 16:51:17 1992
	%%DocumentFonts: (atend)
	%%Pages: 0 1
	%%BoundingBox: 72 31 601 342
	%%EndComments

	gsave
	72 31 moveto
	72 342 lineto
	601 342 lineto
	601 31 lineto
	72 31 lineto
	showpage
	grestore
	%%Trailer
	%%DocumentFonts: Helvetica
\end{filecontents}
%
\documentclass[epj]{svjour}

\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
%\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}

% Various Packages
\usepackage{placeins,cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{microtype}
\usepackage{afterpage}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{url}
\usepackage{booktabs,multirow,longtable}
\usepackage{textcomp}
\graphicspath{{../}{./figures/}}

@@

\begin{document}
	%
	\title{The LHC as a Neutrino-Ion Collider}
%	\subtitle{Do you have a subtitle?\\ If so, write it here}
	\author{
		Juan M. Cruz-Martinez\inst{1},
		Max Fieg\inst{2},
		Tommaso Giani\inst{3,4},
		Peter Krack\inst{3,4},
		Toni M\"akel\"a\inst{5},
		Tanjona R. Rabemananjara\inst{3,4},
		Juan Rojo\inst{3,4}
	}
	\titlerunning{The LHC as a Neutrino-Ion Collider}
	\authorrunning{Juan M. Cruz-Martinez et al.}
	\institute{
		CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland  \and
		Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA \and
		Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam \and
		Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands \and
		National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland
	}
	%
	\date{Received: date / Revised version: date}
	\abstract{
		Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
		in the forward (beam) direction, characterised by energies of up to several TeV.
		%
		The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
		signals that this hitherto ignored particle beam is now available for scientific inquiry.
		%
		Here we quantify the impact that neutrino deep-inelastic scattering (DIS)
		measurements at the LHC would have
		on the parton distributions (PDFs) of protons and heavy nuclei.
		%
		We generate projections for DIS structure functions
		for FASER$\nu$ and SND@LHC at Run III,
		as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
		to be  hosted at the proposed
		Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
		%
		We determine that up to one million electron- and muon-neutrino DIS interactions
		within detector acceptance can be expected by the end of the HL-LHC,
		covering a kinematic region in $x$ and $Q^2$ overlapping with that
		of the Electron-Ion Collider.
		%
		Including these DIS projections into
		global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
		and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
		for strangeness and the up and down valence PDFs.
		%
		We show that LHC neutrino data enables improved theoretical
		predictions for core processes at the HL-LHC, such as Higgs and weak gauge
		boson production.
		%
		Our analysis demonstrates that exploiting the LHC neutrino beam effectively
		provides CERN with a ``Neutrino-Ion Collider''
		without  requiring modifications in its accelerator infrastructure.
		%
		\PACS{
			{12.38.-t}{Quantum chromodynamics}   \and
			{24.85.+p}{Quarks, gluons, and QCD in nuclear reactions}
		} % end of PACS codes
	}

	\maketitle
	\setcounter{tocdepth}{3}
	\tableofcontents

	\input{sec-introduction}
	\input{sec-dis-pseudodata}
	\input{sec-results}
	\input{sec-pheno}
	\input{sec-summary}
	\appendix
	\input{app-faser.tex}
	\input{app-nuclearPDFs.tex}

	\bibliographystyle{utphys}
	\bibliography{main.bib}
